Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-08 draft.tex
version of functoriality finished

@@

This complex $\clies(\fg,\cliels(\fh)_f)$ encodes the deformation theory for $L_\infty$ maps around the map $f$.
That is, in a sufficiently sophisticated geometric setting, it is the tangent complex to the mapping space of $L_\infty$ maps from $\fg$ to~$\fh$.
One should view $f$ as the basepoint for this tangent complex.
Due to the splitting $\cliels(\fg) = k \oplus \overline{\cliels(\fg)}$,
we have a decomposition
\begin{align*}
\clies(\fg,\cliels(\fh)_f) 
&\cong \cliels(\fh) \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)\\
&\cong k \oplus \overline{\cliels(\fh)} \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)
\end{align*}
which plays a crucial role in our argument.

@@

@@

\owen{Point out how to use LQT map and deduce existence of $\EE_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^*_c$}

@@

First, as discussed in Section~\ref{sec: dfn of centralizer fact alg},
given $L_\infty$ maps $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms,
we obtain canonical $L_\infty$ maps
\[
\tilde{f}: \Omega^*_c(V) \otimes \fg \rightsquigarrow \Omega^*_c(V) \otimes \fh
\]
and
\[
\tilde{g}: \Omega^*_c(V) \otimes \fh \rightsquigarrow \Omega^*_c(V) \otimes \fl
\]
for each open set~$V$,
which are functorial in opens.
These $L_\infty$ maps correspond to maps of their Lie algebra chains and hence we obtain
\[ 
\mathbf{f}: \bU_n \fg \to  \bU_n \fh \quad \text{and} \quad \mathbf{g}: \bU_n \fh \to  \bU_n \fl,
\]
maps between their enveloping factorization algebras.

Recall from Section~\ref{sec: review of linfty} the natural decomposition 
\[
\clies(\fg,(\cliels(\fh)_f)) \cong k \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)
\]
and that the summand $k$ corresponds to (scalar multiples of) the defining map~$f: \fg \rightsquigarrow \fh$.
(Abusively, here $f$, $\fg$, and $\fh$ are generic and are not those appearing in the theorem we are proving here.)
Hence, any element $\varphi$ in $\bZ_n(f)$, for instance, has the form
\[
\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}
\]
where $\lambda_\varphi \in k$, encoding the component in the first summand, and $\overline{\varphi}$ denotes the component in the second summand.

\begin{dfn}\label{def:comp}
For any \emph{connected} open set $W$, we define the composition 
\[
\bZ_n(g)(W) \otimes \bZ_n(f)(W) \xto{(-\star-)} \bZ_n(g \circ f)(W)
\]
as follows.
For any element
\[
\psi=\lambda_\psi \mathbf{1} +\overline{\psi} \in \bZ_n(g)(W) = \clies(\fh \otimes \Omega(W), \bU_n \fl (W)  )
\]
and any element
\[
\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}\in \bZ_n(f)(W) = \clies(\fg \otimes \Omega(W), \bU_n \fh (W)  ),
\] 
set
\[
\psi \star \varphi =  \lambda_{\psi} \lambda_{\varphi} \mathbf{1}+
\lambda_\psi g\circ \overline{\varphi} + \lambda_{\varphi} \overline{\psi} \circ \iota_W \circ f +\overline{\psi} \circ \iota_W \circ \overline{\varphi} 
\]
where the inclusion $\iota_W: \Omega^*_c(W) \hookrightarrow \Omega^*(W)$ is extended in the obvious, functorial way to this setting.
\end{dfn}

@@

For a disconnected open $U=\coprod\limits_{i\in I}U_i$, 
where the $U_i$ are the connected components of $U$,  
we define the composition $(-\star-)$ by applying it to each component and then applying the structure map of the factorization algebras,
as follows.
For any $\psi \in \bZ_n(f)(U)$ and $\varphi \in \bZ_n(g)(U)$,
we write 
\[
\varphi = \mathop{\bigotimes}\limits_{i\in I} \varphi_i
\]
where $\varphi_i \in \bZ_n(g)(U_i)$ and likewise $\psi= \mathop{\bigotimes}\limits_{i\in I} \psi_i$.
Then we define
\begin{equation} 
\label{eqdef:staronnonconnected}
\psi \star \varphi \, := \mu_{\fl} \circ \Big( \bigotimes\limits_{i\in I} (\psi_i \star \varphi_i)\Big) 
\end{equation}
where $\mu_{\fl}: \mathop{\bigotimes}\limits_{i\in I} \bU_n \fl (U_i) \cong \bU_n \fl (U)$ 
is the structure map.

\owen{I pooped out here.}

\begin{lmm}
\label{L:compisfacmap} 
The composition $$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) \otimes 
\clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big)
\stackrel{(-\star-)}\longrightarrow 
\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)
$$
 is a morphism of factorization algebras.
\end{lmm}

\begin{proof}

\end{proof}
The composition is compatible with the augmentation splitting. Precisely, we have
\begin{lmm}\label{L:compisaugmented} For any $\varphi \in \clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big)$,
$\psi \in \clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)$
 One has the following equalities  :
 \begin{align}
  \overline{\psi\star \varphi} \;= \;\mathbf{1}\star \overline{\varphi} +\overline{\psi}\star \mathbf{1} +\overline{\psi}\star \overline{\varphi} 
  & \quad\mbox{ (in  $\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $)}\\
 \mathbf{1}\star \varphi \;=\;  (\lambda_\varphi \mathbf{1}, g\circ \overline{\varphi})\qquad
  &\quad\mbox{ (in  $k  \oplus \overline{\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)}$)}\\
  \psi \star \mathbf{1}\;=\; (\lambda_\psi \mathbf{1}, \overline{\psi} \circ f) \qquad
  &\quad\mbox{ (in  $k  \oplus \overline{\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big)}$).}
 \end{align}
 In particular, $\mathbf{1} \star \mathbf{1} =\mathbf{1}$.
\end{lmm}
\greg{maybe I shoudl use the notation $\mathbf{1}_{\mathbf{f}}$, $\mathbf{1}_{\mathbf{g}}$, $\mathbf{1}_{\mathbf{g\circ f}}$ to differentiate 
the various spaces in which leaves the units and avoid possible confusion...?}
\begin{proof}

\end{proof}
The composition is asscoiative in the following sense.
\begin{lmm}\label{L:compisassociative} Let $\fg \stackrel{f}\to \fh$, $\fh \stackrel{g}\to \fl$ and $\fl \stackrel{h}\to \fk$ be maps of $L_\infty$-algebras.
 Then, we have, for any $\varphi \in \clies\big(\fg\otimes \Omega, \cliels(\fh \otimes \Omega_c) \big)$, 
  $\psi \in \clies\big(\fh\otimes \Omega, \cliels(\fl \otimes \Omega_c) \big)$ and  
  $\gamma \in \clies\big(\fl\otimes \Omega, \cliels(\fk \otimes \Omega_c) \big)$, the equality 
  \[ (\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi) \quad \mbox{ in 
  $\clies\big(\fg\otimes \Omega, \cliels(\fk \otimes \Omega_c) \big)$.}  \]
\end{lmm}
\begin{proof}

\end{proof}

\begin{lmm}\label{L:NatPptyofComp}
 The following diagram of factorization algebras 
 \[\tiny \begin{tikzcd}
 \clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
 \otimes  \clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) 
 \otimes \cliels(\fg \otimes \Omega_c  \big) \arrow[rd, "(-\star-)\otimes \id"]
 \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
 & \clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
 \otimes \cliels(\fg \otimes \Omega_c  \big)
 \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
 \otimes \cliels(\fh \otimes \Omega_c  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c  \big). 
\end{tikzcd}\]
 is commutative.
\end{lmm}

\begin{proof}
\end{proof}

\begin{proof}[Proof of Theorem~\ref{T:compcentralizer}]
By universal property of centralizers, the canonical map~\eqref{eqdef:canonicaltocentralizers}  
is the unique\footnote{it is unique in the $\infty$-categorical 
sense, that is there is a contractible space of choices for it} map 
\[ \Upsilon: {\frak Z}_n(\UU_n g) \otimes {\frak Z}_n(\UU_n f) \longrightarrow {\frak Z}_n\big(\UU_n (g\circ f)\big)\] 
of $\EE_n$-algebras which makes the following diagram
\begin{equation}\label{eq:comdiagforcentralizercomput}\small
 \xymatrix{
&   &&  
{\frak Z}_n\big(\UU_n (g\circ f) \big) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{\UU_n (g\circ f)}}\\
&{\frak Z}_n(\UU_n g) \otimes  {\frak Z}_n(\UU_n f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{\UU_n f}}
&& (1)
& & \\
\UU_n \fg \ar[ur]_{1^{\otimes 2}\otimes \id_{\UU_n \fg}} \ar@/_{1pc}/[rrd]^{\UU_n f} \ar@/^{6pc}/[rrruu]_{1\otimes \id_{\UU_n \fg}} &&&
{\frak Z}_n(\UU_n g) \otimes \UU_n \fh \ar[rd]^{\ev_{\UU_n h}}  &\\
&& \UU_n \fh \ar[rr]^{\UU_n g} \ar[ur]^{1\otimes \id_{\UU_n \fh}} && \UU_n \fl .}
\end{equation}
commutative (since $\UU_n (g\circ f) = \UU_n g\, \circ \, \UU_n f $;  the commutativity of the lower part of the diagram being by definition of centralizers).

By Theorem~\ref{thm:centralizerfactorization}, we know that the factorization algebra models for the centralizers are given by the respective Chevalley-Eilenberg cochain factorizations algebras 
(Definition~\ref{dfn:CEofFact}) $\clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) $, 
$\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ and $\clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) $ 
equipped with the evaluations maps are given by $\ev_{\mathbf{f}}$, $\ev_{\mathbf{g}}$ and $\ev_{\mathbf{g}\circ \mathbf{f}}$. We are thus left 
to prove that the same  diagram as~\eqref{eq:comdiagforcentralizercomput}, where we replace the objects and maps by their factorization analogue and $\Upsilon$
by $(-\star-)$, is commutative in factorization algebras.

Thus the map $(-\star-)$ represents the canonical map of factorization algebras 
$ {\frak Z}(\mathbf{g}) \otimes {\frak Z}(\mathbf{f}) \longrightarrow {\frak Z}(\mathbf{g}\circ \mathbf{f})$ which by proposition~\ref{P:PtyCenter} lifts
into an $E_1$-algebra map. It remains to check that the structure is on the nose an augmented associative algebra structure.
The augmentation and unitality are provided by Lemma~\ref{L:compisaugmented} (since in our case $f=g=\id-A$). 
It remains to prove associativity. It follows from Lemma~\ref{L:compisassociative}. 
The commutativity of the lower square and triangle of the diagram follows from Lemma~\ref{L:ComTriangCent}.
\end{proof}

\greg{To add: remark that it implies the corollary~\ref{thm: center} and so.}

@@

In this section, we describe a relationship of our model of the $\EE_n$-center with a certain topological field theory. 
This theory admits a natural description via the AKSZ formalism \cite{AKSZ}, which we briefly recount now.

For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as {\em topological BF theory}.
Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
When $N$ is compact, the classical moduli space underlying this topological field theory can be described as the following mapping space 
\begin{equation} \label{stack1}
{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
\end{equation}
where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
Via the obvious $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, the AKSZ formalism equips the mapping space with a $(-1)$-shifted symplectic structure. 
Classically, on manifolds without boundary, this is the complete description of topological BF theory in the Batalin--Vilkovisky formalism \cite{BV}.

Now, suppose $N$ has non-empty boundary $\partial N \ne 0$.
Then, (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
However, the AKSZ construction equips 
\[
{\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
\]
with a $0$-shifted symplectic structure. 
Moreover, the restriction map 
\[
{\rm Map}(N_{\rm dR} , {\rm T}^* [n] {\rm B} G) \to {\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
\]
is a Lagrangian morphism. 
%Perturbatively, this mapping stack represents the restriction of the fields to the boundary.

For BF theory, this $0$-shifted symplectic manifold admits another natural Lagrangian. 
In terms of mapping stacks, it is given by considering maps from $\partial N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
\[
{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e [n] {\rm B}G) .
\]
Then, by abstract maneuvers \brian{reference} the following fiber product
\[
\begin{tikzcd}
X \ar[r] \ar[d] & {\rm Map} (N , {\rm T}^* [n] {\rm B} G) \ar[d] \\
{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e  [n] {\rm B}G) \ar[r] & {\rm Map}(\partial N_{\rm dR} , {\rm T}^*[n]  {\rm B}G)
\end{tikzcd}
\]
is equipped with a $(-1)$-shifted symplectic structure. 
Heuristically, the classical observables are given by functions on the $(-1)$-shifted symplectic space $X$.

>>>>

{\em Nota bene:}\/ For concision --- and since it is essentially the only kind of map we deal with in this paper --- we simply write $f: \UU_n \fg \to \UU_n \fh$ for the map $\UU_n(f)$ arising from the $L_\infty$ map $f: \fg \rightsquigarrow \fh$.
Likewise, we write ${\frak Z}_n(f)$ instead of~${\frak Z}_n(\UU_n f)$.

@@

This complex $\clies(\fg,\cliels(\fh)_f)$ encodes the deformation theory for $L_\infty$ maps around the map~$f$.
In concrete terms, the Hom-complex $\Hom^\bullet (\cliels(\fg), \cliels(\fh))$ describes the ``linear space'' of linear maps between those complexes.
Hence, if we pick a particular map, such as $f$, the underlying graded space of its ``tangent space''
\[
T_f \Hom^\bullet (\cliels(\fg), \cliels(\fh))
\]
is naturally isomorphic to the ambient linear space,
but the basepoint $f$ of this tangent space is remembered in the twisted differential $\d_\Hom + [f,-]$.
In a sufficiently sophisticated geometric setting, there is a moduli space of $L_\infty$ maps from $\fg$ to~$\fh$,
and $\clies(\fg,\cliels(\fh)_f)$ is this tangent complex with basepoint~$f$.

Due to the splitting $\cliels(\fg) = k \oplus \overline{\cliels(\fg)}$,
we have a decomposition
\begin{align*}
\clies(\fg,\cliels(\fh)_f) 
&\cong \cliels(\fh) \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)\\
&\cong k \oplus \overline{\cliels(\fh)} \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)
\end{align*}
which plays a crucial role in our argument.

@@

We apply our central result to important classes of Lie algebras: 
abelian, semisimple, and free.
We also indicate the large $N$ behavior of enveloping algebras for the infinite families $\frak{gl}_N$, $\frak{sp}_N$, and $\frak{so}_N$,
by exploiting the Loday-Quillen-Tsygan theorem and its cousins.

@@

\owen{Point out how to use LQT map and deduce existence of $\EE_n$ algebra structure on a shifted copy of cyclic cohomology of~$\Omega^*_c$. Also do the Loday versions that use the other infinite series.}

@@

First, as discussed in Section~\ref{sec: dfn of centralizer fact alg},
given $L_\infty$ maps $f: \fg \to \fh$ and $g: \fh \to \fl$,
we obtain canonical $L_\infty$ maps
\[
\tilde{f}: \Omega^*_c(V) \otimes \fg \rightsquigarrow \Omega^*_c(V) \otimes \fh
\]
and
\[
\tilde{g}: \Omega^*_c(V) \otimes \fh \rightsquigarrow \Omega^*_c(V) \otimes \fl
\]
for each open set~$V$,
which are functorial in opens.
These $L_\infty$ maps correspond to maps of their Lie algebra chains and hence we obtain
\[ 
\mathbf{f}: \bU_n \fg \to  \bU_n \fh \quad \text{and} \quad \mathbf{g}: \bU_n \fh \to  \bU_n \fl,
\]
maps between their enveloping factorization algebras.
The composite $L_\infty$ maps $g \circ f: \fg \rightsquigarrow \fl$ determines canonically a map
\[
\mathbf{g \circ f}: \bU_n \fg \to \bU_n \fl
\]
of factorization algebras.

Now recall that
\[
\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f) = \Hom^\bullet(\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fh)_f)
\]
and similarly for the centralizer~$\bZ_n(g)$.
As linear maps compose and hence produce pairings between Hom-complexes,
we expect it should be obvious to produce the desired map
\begin{align*}
\Hom^\bullet(\cliels(\Omega^* \otimes \fh), \cliels(\Omega^*_c \otimes \fl)) 
\otimes \Hom^\bullet(&\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fh))\\
 &\xto{{\rm comp}} \Hom^\bullet(\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fl)).
\end{align*}
This map is easily concocted thanks to the canonical inclusion $\iota_V: \Omega^*_c(V) \hookrightarrow \Omega^*(V)$ for any open set~$V$.
Indeed, for any $\varphi \in \Hom^\bullet(\cliels(\Omega^* \otimes \fg), \cliels(\Omega^*_c \otimes \fh))$,
the composite $\iota_V \circ \varphi|_V$ lives in $\Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg), \cliels(\Omega^*(V) \otimes \fh))$,
and so we define
\[
{\rm comp}(\psi, \varphi)|_V = \psi|_V \circ \iota_V \circ \varphi|_V \in \Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg), \cliels(\Omega^*_c(V) \otimes \fl))
\]
on each open~$V$.
This construction is functorial in the open $V$ and hence determines the desired map ${\rm comp}$.

This construction is {\em almost} what we need, 
but it does not take into account $f$ or $g$.
To do that, we need to recall that we view these Hom-complexes as describing the tangent spaces where the maps label the basepoints.
Once we do, a modest revision of formula above works.

Recall from Section~\ref{sec: review of linfty} the natural decomposition 
\[
\clies(\fg,(\cliels(\fh)_f)) \cong k \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)
\]
and that the summand $k$ corresponds to (scalar multiples of) the defining map~$f: \fg \rightsquigarrow \fh$.
(Abusively, here $f$, $\fg$, and $\fh$ are generic and are not those appearing in the theorem we are proving here.)
Hence, any element $\varphi$ in $\bZ_n(f)$, for instance, has the form
\[
\varphi =\lambda_\varphi {\bf 1_f} +\overline{\varphi}
\]
where $\lambda_\varphi \in k$ encodes the component in the first summand and $\overline{\varphi}$ denotes the component in the second summand.

\begin{dfn}
\label{def:comp}
For any open set $V$, we define the composition 
\[
\bZ_n(g)(V) \otimes \bZ_n(f)(V) \xto{(-\star-)} \bZ_n(g \circ f)(V)
\]
as follows.
For any element
\[
\psi=\lambda_\psi {\bf 1_g} +\overline{\psi} \in \bZ_n(g)(V) = \clies(\fh \otimes \Omega^*(V), (\bU_n \fl (V))_g  )
\]
and any element
\[
\varphi =\lambda_\varphi {\bf 1_f} +\overline{\varphi}\in \bZ_n(f)(V) = \clies(\fg \otimes \Omega^*(V), (\bU_n \fh (V))_f  ),
\] 
set
\[
\psi \star \varphi =  
\lambda_{\psi} \lambda_{\varphi} \mathbf{1_{g\circ f}}
+ \lambda_\psi \,g \circ \overline{\varphi} 
+ \lambda_{\varphi}\, \overline{\psi} \circ \iota_V \circ f 
+\overline{\psi} \circ \iota_V \circ \overline{\varphi} 
\]
where the inclusion $\iota_V: \Omega^*_c(V) \hookrightarrow \Omega^*(V)$ is extended in the obvious, functorial way to this setting.
\end{dfn}

@@

\owen{Greg gave the above definition for {\em connected} open sets and then extended it to disconnected open sets b an explicit formula. 
I don't see why that's necessary (but maybe I'm being silly), so I've cut it as I am aiming for concision.
We can revive Greg's argument if needed.}

By direct inspection this construction is functorial in opens and respects structure maps.

\begin{lmm}
\label{L:compisfacmap} 
The composition 
\[
 \bZ_n(g) \otimes  \bZ_n(f) \xto{(-\star-)}  \bZ_n(g \circ f)
\]
 is a map of factorization algebras.
\end{lmm}

It is also straightforward to check the following properties,
which we record as a trio of lemmas.
The first is about associativity.

\begin{lmm}
\label{L:compisassociative} 
Let $f: \fg \rightsquigarrow \fh$, $g: \fh \rightsquigarrow \fl$ and $h: \fl \rightsquigarrow \fk$ be maps of $L_\infty$-algebras.
For any $\varphi \in \bZ_n(f)$, $\psi \in \bZ_n(g)$, and $\gamma \in \bZ_n(h)$,  
the equality 
\[ 
(\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi)  
\]
holds in $\clies\big(\fg\otimes \Omega^*, (\bU_n \fk)_{h \circ g \circ f} \big)$.
\end{lmm}

The second verifies that augmentations are preserved.

\begin{lmm}
\label{L:compisaugmented} 
For any $\varphi \in \bZ_n(g)$ and
$\psi \in \bZ_n(f)$,
the following equalities 
\begin{align}
\overline{\psi\star \varphi} &\;= \;\mathbf{1_g}\star \overline{\varphi} +\overline{\psi}\star \mathbf{1_f} +\overline{\psi}\star \overline{\varphi} \\
\mathbf{1_g}\star \varphi &\;=\;  (\lambda_\varphi \mathbf{1_{g \circ f}}, g\circ \overline{\varphi})\\
\psi \star \mathbf{1_f} &\;=\; (\lambda_\psi \mathbf{1_{g \circ f}}, \overline{\psi} \circ f) 
\end{align}
hold in $\bZ_n(g \circ f) = k  \oplus \overline{\clies\big(\fg \otimes \Omega^*, (\bU_n \fl)_{g \circ f}  \big)}$.
In particular, $\mathbf{1_g} \star \mathbf{1_f} =\mathbf{1_{g \circ f}}$.
\end{lmm}

The third is about compatibility with the pairings that characterize the centralizers.

\begin{lmm}
\label{L:NatPptyofComp}
 The diagram of factorization algebras 
 \[
 \small
 \begin{tikzcd}
 \bZ_n(g)
 \otimes  \bZ_n(f) \otimes \bU_n \fg \arrow[rd, "(-\star-)\otimes \id"]
 \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
 & \bZ_n(g \circ f)
 \otimes \bU_n \fg
 \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
\bZ_n(g) \otimes \bU_n \fh  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  
 & \bU_n \fl. 
\end{tikzcd}
\]
 is commutative.
\end{lmm}

\owen{I did not include a proof because I think it's immediate once you write down the formulas,
but maybe I'm overly optimistic.}

\begin{proof}[Proof of Theorem~\ref{T:compcentralizer}]
By the universal property of centralizers, 
the canonical map~\eqref{eqdef:canonicaltocentralizers} is the unique map 
\[ 
\Upsilon: {\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f)
\] 
of $\EE_n$ algebras (up to a contractible space of choices) that makes the following diagram
\begin{equation}
\label{eq:comdiagforcentralizercomput}
\xymatrix{
&   &&  
{\frak Z}_n(g\circ f) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{g\circ f}}\\
&{\frak Z}_n(g) \otimes  {\frak Z}_n(f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{f}}
&& (\dagger)
& & \\
\UU_n \fg \ar[ur]_{1^{\otimes 2}\otimes \id_{\UU_n \fg}} \ar@/_{1pc}/[rrd]^{f} \ar@/^{6pc}/[rrruu]_{1\otimes \id_{\UU_n \fg}} &&&
{\frak Z}_n(g) \otimes \UU_n \fh \ar[rd]^{\ev_{h}}  &\\
&& \UU_n \fh \ar[rr]^{g} \ar[ur]^{1\otimes \id_{\UU_n \fh}} && \UU_n \fl .
}
\end{equation}
commutative.
%Note that the lower part of the diagram commutes by definition of centralizers.

The diagram above is model-independent,
but we will check that the analogous diagram~\eqref{eq:comdiagforcentralizercomput} commutes when we use our models $\bU_n \fg$, $\bZ_n(f)$, and so on for the objects and when we use our factorization maps $\ev_{{\bf f}}$ (for $\ev_f$), ${\bf 1}$ (for the unit elements $1$),  and so on.
In particular, we use $(-\star-)$ for~$\Upsilon$.

The commutativity of the bottom square and bottom triangle follows from Lemma~\ref{L:ComTriangCent}.
The square with ($\dagger$) in the middle follows from Lemma~\ref{L:NatPptyofComp}.
The top triangle commutes by Lemma~\ref{L:compisassociative}. 
Thus we have shown statement~(1) of the theorem.

To prove statement~(2), we note that we have the associative multiplication.
Since here $f=g=\id_A$, we have the unitality,
while the augmentation is provided by Lemma~\ref{L:compisaugmented}.
\end{proof}

@@

In this section, we describe a relationship between our model of the $\EE_n$-center and a certain topological field theory. 
This theory admits a natural description via the AKSZ formalism \cite{AKSZ}, which we briefly recount now.

For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as {\em topological BF theory}.
Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
When $N$ is compact, the classical moduli space underlying this topological field theory can be described as the following mapping space 
\begin{equation} \label{stack1}
{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
\end{equation}
where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
Via the canonical $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, the AKSZ construction equips the mapping space with a $(-1)$-shifted symplectic structure. 
Classically, on manifolds without boundary, this produce describes topological BF theory in the Batalin--Vilkovisky formalism~\cite{BV}.

Now, suppose $N$ has non-empty boundary $\partial N \ne 0$.
Then, (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
However, the AKSZ construction equips 
\[
{\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
\]
with a $0$-shifted symplectic structure. 
Moreover, the restriction map 
\[
{\rm Map}(N_{\rm dR} , {\rm T}^* [n] {\rm B} G) \to {\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
\]
is a Lagrangian morphism. 
\owen{Somewhere say that $N$ and $\partial N$ are still compact here.}
%Perturbatively, this mapping stack represents the restriction of the fields to the boundary.

For BF theory, this $0$-shifted symplectic manifold admits another natural Lagrangian. 
In terms of mapping stacks, it is given by considering maps from $\partial N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
\[
{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e [n] {\rm B}G) .
\]
Then, by higher abstract nonsense \brian{reference} the fiber product
\[
\begin{tikzcd}
X \ar[r] \ar[d] & {\rm Map} (N , {\rm T}^* [n] {\rm B} G) \ar[d] \\
{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e  [n] {\rm B}G) \ar[r] & {\rm Map}(\partial N_{\rm dR} , {\rm T}^*[n]  {\rm B}G)
\end{tikzcd}
\]
is equipped with a $(-1)$-shifted symplectic structure. 
Heuristically, the classical observables are given by functions on the $(-1)$-shifted symplectic space $X$.
\owen{I'm not sure it's a heuristic. I think we could say that we interpret functions on $X$ as the classical observables for the classical field theory with this boundary condition.}
